Survival Analysis of iFixit's Online Question and Answer Forum

### 2017-11-01 presentation/presentation.tex
added acknowledgements slide

%Information to be included in the title page:
\title{Survival Analysis of iFixit's Online Question and Answer Forum}
\author{Lisa Oshita}
\institute{Bill and Linda Frost Fund\\
Frost Research Fellow\\
Recipient of the Frost Undergraduate Student Research Award}
\date{2017}

@@

  \begin{itemize}
      \item 7,760 questions posted between April 8, 2017 to July 7, 2017
      \item 63.8\% recieved an answer by the download date
      \item Median survival time, the time at which 50\% of the questions in the data recieved an answer, is 9.16 hours
  \end{itemize}

@@

>>>>

%Information to be included in the title page:
\title{Survival Analysis of iFixit's Online Question and Answer Forum}
\author{Lisa Oshita}
\institute{California Polytechnic State University, San Luis Obispo}
\date{2017}

@@

  \begin{itemize}
      \item 7,760 questions posted between April 8, 2017 to July 7, 2017
      \item 63.8\% received an answer by the download date
      \item Median survival time, the time at which 50\% of the questions in the data received an answer, is 9.16 hours
  \end{itemize}

@@

%background information on iFixit
\begin{frame}
\frametitle{Acknowledgements}
  \begin{itemize}
    \item Dr. Shannon Pileggi
    \item Anthony Pileggi
    \item Bill and Linda Frost Fund\\
          Frost Research Fellow\\
          Recipient of the Frost Undergraduate Student Research Award
  \end{itemize}
\end{frame}
